### 2014-04-22 Response_to_R0_Reviews.tex

\documentclass[10pt]{article}
\usepackage{graphicx}
\pagestyle{empty}
\topmargin=-0.75in
\oddsidemargin=0.0in
\textwidth=6.5in
\textheight=9.5in
\parindent=0.0in
\parskip=10pt

\begin{document}

\section*{Response to Reviews}

We thank both reviewers for their insight and comments on the original
submission of our manuscript.  Overall, well agree with all of the comments
that were provided, and we have made edits to our original manuscript that we
feel respond to all of this feedback.  We have provided a detailed response to
the review below, with the original comments italicized, and the responses in
normal text.  The revised manuscript has significant additions indicated with
bold text and removed text has been struck through.

@@

\textit{Reviewer: 2}

\textit{Comments to the Author}

\textit{This is a nice study of ARFI imaging of the prostate that compares ARFI images
to MRI. Three areas of the paper could be improved:}

\begin{itemize}
    \item \textit{The ellipsoidal prostate volume estimate from pathology could be
        improved by using the prostate segmentation on each of the whole mount
        pathology slides to align the data to the MRI prostate surface. The
        volume comparison is further complicated by the shrinkage of the
        prostate after fixation.}

   Our ellipsoidal approximation of the prostate volume is a rough
   approximation from the surgical pathology reports, but we felt it was our
   best metric to approximate prostate size for the following reasons:

   \begin{itemize}
        \item The gross surgical pathology mesaurements used to make the
            ellipsoidal volume approximation were done after peri-prostatic
            tissue was dissected away, but before formalin fixation, avoiding
            the complication of tissue shrinkage associated with formalin
            fixation, which our pathologists estimated could be as much as 30\%
            of the prostate volume.
        \item Whole mount histology slides were explored for this purpose, but
            they suffer from post-fixation contraction, $\sim$ 3 mm slice
            thickiness, and slice tearing and folding that compromise accurate
            cross-sectional area representations on a single slide.
            Additionally, the whole mount histology slides require some degree
            of image registration due to their arbitrary orientation on the
            slides, adding another source of error.
    \end{itemize}

    Given the reasons above, we decided to use the tri-axial measurements in
    gross pathologic evaluation as our closest approximation of the glands
    total volume as it would have been during MR and ultrasound imaging.  We
    have added text to Section II.B that details this choice for estimating our
    prostate volumes:

    \textbf{\input{path_volume_choice}}

### 2014-04-23 intro.tex
Stephen's comments
updated response about vibro-elastography

PCa diagnosis usually begins by screening with prostate specific antigen (PSA)
and digital rectal examination (DRE).  More definitive diagnosis can be made by
random transrectal ultrasound (TRUS)-guided biopsies, which are then used to
provide the clinician with the proper Gleason score. The combination of these
factors, as well as staging, determines the appropriate therapy and prognosis.

@@

The goal of this study is to evaluate the ability of ARFI imaging to delineate
prostate zonal anatomy, specifically central gland and total prostate gland
\invivo as compared to T2WI MR at 3T using an endorectal coil.
Section~\ref{sect:background} provides an overview of MR and ARFI imaging in
the prostate and an overall clinical motivation for prostate imaging.
Section~\ref{sect:methods} describes the methods used to experimentally-acquire
our imaging data, process the gross pathological specimens post radical
prostatectomy, and image process our datasets.  The results of our analysis,
including gross pathology and imaging prostate axis and volume estimates, are
presented in Section~\ref{sect:results}, along with a statistical analysis of
the bias and variability associated with each imaging modalities measurements,
all of which is discussed in Section~\ref{sect:discussion}.

>>>>

PCa diagnosis usually begins by screening with a prostate specific antigen (PSA)
test and digital rectal examination (DRE).  More definitive diagnosis can be made by
random transrectal ultrasound (TRUS)-guided biopsies, which are then used to
provide the clinician with the proper Gleason score. The combination of these
factors, as well as staging, determines the appropriate therapy and prognosis.

@@

The goal of this study is to evaluate the ability of ARFI imaging to delineate
prostate zonal anatomy, specifically central gland and total prostate gland
\invivo as compared to T2WI MR at 3T using an endorectal coil.
\input{intro_vibroelastography}
Section~\ref{sect:background} of this manuscript provides an overview of MR and
ARFI imaging in the prostate and an overall clinical motivation for prostate
imaging.  Section~\ref{sect:methods} describes the methods used to
experimentally-acquire our imaging data, process the gross pathological
specimens post radical prostatectomy, and image process our datasets.  The
results of our analysis, including gross pathology and imaging prostate axis
and volume estimates, are presented in Section~\ref{sect:results}, along with a
statistical analysis of the bias and variability associated with each imaging
modalities measurements, all of which is discussed in
Section~\ref{sect:discussion}.
